---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jpaddr

<!-- badges: start -->
<!-- badges: end -->

jpaddr is a R package for Japanese address normalization.

## Credits

This package is based on the following projects:

### [geolonia/normalize-japanese-addresses](https://github.com/geolonia/normalize-japanese-addresses)

- Author: [Geolonia](https://www.geolonia.com)
- License: MIT License

### [geolonia/japanese-addresses](https://github.com/geolonia/japanese-addresses)

- Author: [Geolonia](https://www.geolonia.com)
- License: [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/deed.ja)

## Installation

You can install the development version of jpaddr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UchidaMizuki/jpaddr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r library}
library(jpaddr)
```

You need to install the dependent packages first.

```{r jpaddr_install, eval = FALSE}
jpaddr_install()
```

```{r normalize_address}
normalize_address(c("東京都千代田区千代田1-1", "大阪府大阪市北区梅田2-2-2"))
```
